Evolution of ORM Systems: Formal Foundations

### 2013-01-16 doc/description.tex
small fix in add calss description

\paragraph{Add Class} Adding a class is limited to the case when the class has no associations, this is because it simplifies the database migration and because it is a natural way of modeling. Next the transformation $addClass$ has to verify there is no name collision
\begin{align*}
	\mathbf{addClass} : Class \times Application \rightarrow Application \\ 
	addClass(c, a) = \inference{\forall s \in classes(a) : name(s) \neq name(c) \\ \wedge associations(c) = \varnothing }{classes(a) \cup c} \\ \\
	c \lhd Class, a \lhd Applications
\end{align*}

@@

\paragraph{Add Class} The $insertClass$ operation changes the structure of the database schema only, because the $insertAssoc$ transformation needs a mapping function to work properly, which is not part of the $newClass$ definition. The situation reflect the modeling praxis when the structure of a class is defined and then it is associations are created.
\begin{align*}
\mathbf{newClass} : Class \times State \rightarrow State \\
\Psi(s, newClass(c)) = application(s) \circ addClass(c) \\
\Phi(s, newClass(c)) = database(s)  \bullet addTable(\rho(c,d), d) \\ \bullet addColumn(name(c), \{\forall r \in singleProperties(c) | \rho(r,d)\}, d) \\ \bullet addTable(name(c), \{\forall r \in collections(c) | \rho(r,d)\}, d)  
\end{align*}

>>>>

\paragraph{Add Class} Adding a class is limited to the case when the class has no associations, this is because it simplifies the database migration. The transformation $addClass$ has to verify there is no name collision
\begin{align*}
	\mathbf{addClass} : Class \times Application \rightarrow Application \\ 
	addClass(c, a) = \inference{\forall s \in classes(a) : name(s) \neq name(c) \\ \wedge associations(c) = \varnothing }{classes(a) \cup c} \\ \\
	c \lhd Class, a \lhd Applications
\end{align*}

@@

\paragraph{Add Class} The $insertClass$ operation changes the structure of the database schema only, because the $insertAssoc$ transformation needs a mapping function to work properly, which is not part of the $newClass$ definition. The situation reflect the modeling praxis when the structure of a class is defined and then its associations are created.
\begin{align*}
\mathbf{newClass} : Class \times State \rightarrow State \\
\Psi(s, newClass(c)) = application(s) \circ addClass(c) \\
\Phi(s, newClass(c)) = database(s)  \bullet addTable(\rho(c,d), d) \\ \bullet addColumn(name(c), \{\forall r \in singleProperties(c) | \rho(r,d)\}, d) \\ \bullet addTable(name(c), \{\forall r \in collections(c) | \rho(r,d)\}, d)  
\end{align*}
